Fluent statistical computing interfaces for biological data analysis

### 2020-03-24 Rmd/05-embeddings.Rmd
spelling

We have implemnted the above design as an open source R package 
called `liminal` [@baseR]. The package allows analysts to constuct
concatenated visualisations, via the
Vega-Lite grammar of interactive graphics (using `vegawidget` package)
and provides an interface for constructing brushes and manipulating tour paths
using the `shiny` and `tourr` packages. `liminal` also provides a stand-alone
interface to the tour, in addition to the linked scatterplot interfaces 
discussed above. Below we display the `liminal` API, and our approach to
generating tour paths and user interactions.

>>>>

We have implemented the above design as an open source R package 
called `liminal` [@baseR]. The package allows analysts to construct
concatenated visualisations, via the
Vega-Lite grammar of interactive graphics (using `vegawidget` package)
and provides an interface for constructing brushes and manipulating tour paths
using the `shiny` and `tourr` packages. `liminal` also provides a stand-alone
interface to the tour, in addition to the linked scatterplot interfaces 
discussed above. Below we display the `liminal` API, and our approach to
generating tour paths and user interactions.
